CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

```{r plot.discovery}
# plot discovery and testing
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

```{r second.cohort, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

```{r plot.discovery.Dx}
# plot discovery and testing.  
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

```{r second.cohort.Dx, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

>>>>

## Discovery cohort
```{r plot.discovery}
# plot discovery and testing
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

## Replication cohort
```{r second.cohort, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

## Discovery cohort
```{r plot.discovery.Dx}
# plot discovery and testing.  
ggplot(df_test, aes(Module, -log10(FDR))) + geom_bar(stat='identity', fill=df_test$Module) + theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + coord_flip() + facet_wrap(~Cohort) + ylab(bquote(-log[10]~FDR)) + scale_y_continuous(expand=c(0,0)) + geom_hline(yintercept = -log10(0.05), color="red", linetype="dashed")
```

@@

## Replication cohort
```{r second.cohort.Dx, fig.width=6, fig.height=12}
df_cohort2 = df_test[df_test$Cohort == "NIMH-HBCC",]
df_cohort2$Module = factor(df_cohort2$Module, unique(df_cohort2$Module))
table(df_cohort2$FDR < 0.05)

@@

plot_grid( plotlist = figList, ncol=1)
```
<!---
